---
title: "Article EOL"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  rmarkdown::html_document:
    code_folding: hide
    fig_caption: yes
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: console
---
```{r setup, include=FALSE}
rm(list = ls())
require(tidyverse)
require(data.table)
require(readxl)
require(pander)
library(scales)
require(seacarb)
library(cowplot)
library(scales)
library(kableExtra)
library(RColorBrewer)
library(gridExtra)
library(reshape2)
library(xtable)
library(zoo)
library(lubridate)
library(nlme)
library(lmtest)
library(readr)
library(dygraphs)
library(grid)
library(viridis)
library(animation)
library(directlabels)
library(tibble)
library(xts)
library(stringr)
require("knitr")
library(broom)
library("lmodel2") # modele II regression
#library(plyr)
library(pander)
library(lubridate)
library(tidyr)

#define who is the user and define path
if (Sys.getenv("LOGNAME") == "gattuso") {
  path = "../../pCloud\ Sync/Documents/experiments/exp153_carbonates_point_B/"
  path_sami = "../../pCloud\ Sync/Documents/experiments/exp176_sami/vlfr_ph_data/3_out_ph_sami_seafet/out_deployment/"
}
if (Sys.getenv("LOGNAME") == "samir") {
  path = "../../pCloud Sync/exp153_carbonates_point_B/"
  path_sami = "../../pCloud\ Sync/exp176_sami/vlfr_ph_data/3_out_ph_sami_seafet/out_deployment/"
  path_par ="../../pCloud Sync/Light_Series_Odyssey/par_data/Villefranche/"
}

Sys.setenv(TZ='UTC')

#################### Regression function 

######## To add regression line on ggplots
# use as annotate(aes(x = 25, y = 300, label = lm_eqn(lm(y ~ x, df))), parse = TRUE)
# http://stackoverflow.com/questions/7549694/ggplot2-adding-regression-line-equation-and-r2-on-graph
lm_eqn = function(m) {
  l <- list(a = format(coef(m)[1], digits = 2),
      b = format(abs(coef(m)[2]), digits = 2),
      r2 = format(summary(m)$r.squared, digits = 3));
  if (coef(m)[2] >= 0)  {
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2,l)
  } else {
    eq <- substitute(italic(y) == a - b %.% italic(x)*","~~italic(r)^2~"="~r2,l)    
  }
  as.character(as.expression(eq));                 
}

######## function to make regression plot with model I equation in title
ggreg <- function (fit, point_size=2) {
  ggplot(fit$model, aes_string(x = names(fit$model)[2],
                               y = names(fit$model)[1])) +
    geom_point(size = point_size, col = "blue") +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste(title, "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       "; Intercept =",signif(fit$coef[[1]],5 ),
                       "; Slope =",signif(fit$coef[[2]], 5),
                       "; P =",signif(summary(fit)$coef[2,4], 5))) +
    theme(plot.title = element_text(size=7))
}

########### Regression function 
####
# function regression plot with model II equation (MA) in title
## Dans labs ajout de la variable TITRE pour mettre titre avant chaque graphe
ggreg2 <- function (fit, xdata, ydata) { # x and y are the names of the variables
  fit_data <- data.frame(fit$x, fit$y)
  colnames(fit_data) = c(xdata, ydata)
reg <- fit$regression.results[2,] #one selects MA only
intercept <- reg$Intercept
slope <- reg$Slope
  ggplot(data = fit_data, aes_string(x = xdata, y = ydata)) + 
  geom_point(size = 3, col = "blue") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),
              colour = "blue")  + 
  labs(title = paste(titre,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(intercept, 3),
                     "; Slope =", signif(slope, 3),
                     "; P =", signif(fit$P.param, 3),
                     "; n =", (fit$n)))
}

mytheme <- theme_bw() +
  theme(axis.text.x=element_text(size=16, color="black"),
        axis.title.x=element_text(face="bold", size=16),
        axis.text.y=element_text(size=16, color="black"),
        axis.title.y=element_text(face="bold", size=16),
        plot.title = element_text(face="bold", size=14)
)
```

# **Introduction** {.tabset .tabset-pills}

# **Material and methods** 

## **Site description**
EOL buoy (43.682◦ N, 7.319◦ E, 80 m bottom depth) and Point B (43.686◦ N, 7.316◦ E, 85 m bottom depth) stations are located in the NW Mediterranean Sea in the Bay of Villefranche-Sur-Mer, France. The two sites are less than 500 m apart. The area is characterized by the passage of the northern current (Liguro-provencal current) offshore the Bay. This anticlockwise current can form meanders and eddies that can potentially bring open-ocean waters to this site (De Carlo et al., 2013).

Point B station started to sample hydrological measurements in 1957 and integrated the French marine stations network SOMLIT (Service d’Observation en Milieu LITtoral) in 1995 (https://www.somlit.fr). Samplings are based on vertical profiles using a CTD and on discrete seawater samplings (see following part for details). All acquisition data regarding Point B station is weekly based.

EOL (Environment Observable Littoral) buoy is part of the COAST-HF (Coastal OceAn observing SysTem – High Frequency) French national observation network of the physical and biogeochemical dynamics of the coastal ocean, at high frequency (https://coast-hf.fr/). Vertical profiles were used to collect data on a high frequency (≤ 1 hour) basis. 


## **Parameters **
In this study 3 main parameters were analysed: temperature (T, in °C), salinity (S, in PSU) and disolved oxygen (O2, in mL-1.L).



## **Calibration**

# **Results** 
```{r ctd_hydro, echo=TRUE, warning = FALSE, message = FALSE}
readRDS(file = paste0(path, "data/eol/eol_data.rds"))
```

# **Discussion** 
